---
title: "GBIF"
output: html_document
date: "2024-11-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Install packages

```{r}
#install.packages("rgbif")
library(rgbif)
```

Read in the species list

```{r}
species = read.csv("../Raw.Data/species.csv")
```

Getting taxon key/usage key for each species

```{r}
taxon.key=name_backbone_checklist(species$Species)
head(taxon.key)
```

Issues found: 

* Taxodium ascendens and Taxodium distichum are synonyms, may be issue if have distinct microenvironments
* Fraxinus texensis is a synonym for Fraxinus albicans, Fraxinus albicans is not in the data set

Download the data

```{r}
occ_download(pred("hasGeospatialIssue", FALSE), # removes coordinates that are (0,0)
             pred("hasCoordinate", TRUE), # keeps only records with coordinates
             pred("occurrenceStatus","PRESENT"), # removes absent record
             pred("country", "US"), # country 
             pred_in("taxonKey",taxon.key$usageKey), # supplying usagekey
             
             pred_or(pred_lt("coordinateUncertaintyInMeters",10000),
                     pred_isnull("coordinateUncertaintyInMeters")), # coordinate Uncertainty is less than 10000 m or left blank
                  format = "SIMPLE_CSV") # return tsv file of occurrences
```

Citation Info:  
  Please always cite the download DOI when using this data.
  https://www.gbif.org/citation-guidelines
  DOI: 10.15468/dl.t7z4jz
  Citation:
  GBIF Occurrence Download https://doi.org/10.15468/dl.t7z4jz Accessed from R via rgbif (https://github.com/ropensci/rgbif) on 2024-11-22

Check status

```{r}
occ_download_wait('0028832-241107131044228')
```

Download data

```{r}
#d = occ_download_get('0028832-241107131044228', path = "/Users/samanthaworthy/Documents/GitHub/Habitat_Geographic_Ranges/Raw.Data") %>%
  occ_download_import()
```

```{r}
head(d)
```

Way more species than in dataset (143). Many varieties included.

```{r}
sort(unique(d$scientificName))
```

```{r}
abies = d %>%
  filter(genus == "Abies")
```

